% ============================================================
%   Hao Xu  —  Academic CV
%   Compile with:  pdflatex cvhao.tex   (run twice for links)
% ============================================================
\documentclass[11pt, a4paper]{article}

% ── encoding & fonts ────────────────────────────────────────
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}          % Latin Modern — smoother than CM
\usepackage{microtype}        % optical margin alignment + kerning

% ── page layout ─────────────────────────────────────────────
\usepackage[
  top    = 0.50in,
  bottom = 0.50in,
  left   = 0.65in,
  right  = 0.65in
]{geometry}

% ── colour ──────────────────────────────────────────────────
\usepackage[dvipsnames]{xcolor}
\definecolor{navyblue}{RGB}{26, 58, 92}
\definecolor{linkblue}{RGB}{22, 90, 160}
\definecolor{rulecolor}{RGB}{26, 58, 92}

% ── hyperlinks ──────────────────────────────────────────────
\usepackage[
  colorlinks = true,
  urlcolor   = linkblue,
  linkcolor  = linkblue,
  citecolor  = linkblue,
  pdfauthor  = {Hao Xu},
  pdftitle   = {Hao Xu — CV}
]{hyperref}

% ── section headings ────────────────────────────────────────
\usepackage{titlesec}
\titleformat{\section}
  {\large\bfseries\color{navyblue}}  % format
  {}{0pt}                             % label, sep
  {}                                  % before-code
  [\color{rulecolor}\vspace{1pt}\hrule height 0.8pt\vspace{2pt}]  % after-code
\titlespacing{\section}{0pt}{7pt}{3pt}

% ── lists ───────────────────────────────────────────────────
\usepackage{enumitem}
\setlist[itemize]{
  leftmargin = 1.4em,
  itemsep    = 2pt,
  topsep     = 3pt,
  parsep     = 0pt
}
\setlist[enumerate]{
  leftmargin = 1.8em,
  itemsep    = 3pt,
  topsep     = 2pt,
  parsep     = 0pt
}

% ── tables ──────────────────────────────────────────────────
\usepackage{array}
\usepackage{tabularx}
\newcolumntype{L}{>{\raggedright\arraybackslash}X}  % left-flex
\newcolumntype{R}{>{\raggedleft\arraybackslash}p{2.2cm}} % right-date

% ── misc ────────────────────────────────────────────────────
\usepackage{parskip}
\setlength{\parskip}{0pt}
\setlength{\parindent}{0pt}

% ── helper: education entry ──────────────────────────────────
\newcommand{\edentry}[3]{%
  \textbf{#1}\par
  \textit{\small #2}\par
  \vspace{1pt}
  {\small\textit{Research: }#3}
  \vspace{3pt}
}

% ── helper: award entry ──────────────────────────────────────
\newcommand{\awardentry}[2]{%
  \begin{tabularx}{\textwidth}{@{}L@{\hspace{6pt}}R@{}}
    #1 & \textit{\small #2} \\
  \end{tabularx}%
  \vspace{1pt}
}

\pagestyle{plain}

% ============================================================
\begin{document}
% ============================================================

% ── HEADER ──────────────────────────────────────────────────
\begin{center}
  {\fontsize{22}{26}\selectfont\bfseries\color{navyblue} Hao Xu}\\[4pt]
  \small
  \href{mailto:haxu0087@uni.sydney.edu.au}{haxu0087@uni.sydney.edu.au}
  \enspace\textbullet\enspace
  \href{https://scholar.google.com/citations?hl=zh-CN&user=UT4pBpAAAAAJ&view_op=list_works&sortby=pubdate}{Google Scholar}
  \enspace\textbullet\enspace
  \href{https://www.linkedin.com/in/hao-xu-5a1201293}{LinkedIn}
  \enspace\textbullet\enspace
  \href{https://github.com/hao7748}{GitHub}
\end{center}

% ── RESEARCH INTERESTS ──────────────────────────────────────
\section{Research Interests}

\small
Foundation models for decision-making \textbullet{} Partially Observable Markov Decision Processes (POMDPs) \textbullet{} LLM applications in manufacturing and materials science

% ── EDUCATION ───────────────────────────────────────────────
\section{Education}

\edentry%
  {Ph.D.\ in Mathematics and Statistics}%
  {The University of Sydney, Sydney, Australia}%
  {Foundation models for decision-making, POMDPs, and AI/LLM applications
   in manufacturing and materials science.}

\edentry%
  {MPhil in Smart Manufacturing}%
  {HKUST (Guangzhou), Guangzhou, China}%
  {Anomaly detection in industrial manufacturing; high-dimensional data
   processing for point clouds and images.}

\edentry%
  {M.S.\ in Data Science}%
  {City University of Hong Kong, Hong Kong, China}%
  {Deep learning and predictive modeling; attention-based financial sentiment
   analysis and epidemiological mortality monitoring.}

\textbf{B.Eng.\ in Materials Science and Engineering}\par
\textit{\small Chongqing University, Chongqing, China}\par
\vspace{1pt}
{\small\textit{Research: }Materials synthesis, characterization, and failure analysis;
  ODS steels, Mg-based hydrogen storage alloys, and high-voltage testing.
  \textbf{Grade Rank: Top 5\%.}}

% ── PUBLICATIONS ────────────────────────────────────────────
\section{Publications}
\small\textit{* indicates co-first authors; \textsuperscript{\textdagger} indicates corresponding authors.}
\vspace{2pt}

\begin{enumerate}[label={[\arabic*]}, leftmargin=2em, itemsep=4pt]

\item Xiangru Jian*, \textbf{Hao Xu*\textsuperscript{\textdagger}}, Wei Pang*, Xinjian Zhao, Chengyu Tao, Qixin Zhang,
  Xikun Zhang\textsuperscript{\textdagger}, Chao Zhang, Guanzhi Deng, Alex Xue, Juan Du, Tianshu Yu, Garth Tarr,
  Linqi Song, Qiuzhuang Sun, Dacheng Tao.\\
  \textbf{FORGE: Fine-grained Multimodal Evaluation for Manufacturing Scenarios.}\\
  \textit{arXiv preprint arXiv:2604.07413}, 2026.
  \href{https://arxiv.org/abs/2604.07413}{\small[arXiv]}

\item \textbf{Hao Xu*}, Xiangru Jian*\textsuperscript{\textdagger}, Xinjian Zhao*, Wei Pang*, Chao Zhang, Suyuchen Wang,
  Qixin Zhang, Zhengyuan Dong, Joao Monteiro, Bang Liu, Qiuzhuang Sun, Tianshu Yu\textsuperscript{\textdagger}.\\
  \textbf{GraphOmni: A Comprehensive and Extendable Benchmark Framework for Large
  Language Models on Graph-theoretic Tasks.}\\
  \textit{International Conference on Learning Representations (ICLR)}, 2026.
  \href{https://arxiv.org/abs/2504.12764}{\small[arXiv]}

\item Chengyu Tao, \textbf{Hao Xu}, Juan Du\textsuperscript{\textdagger}.\\
  \textbf{F2PAD: A General Optimization Framework for Feature-Level to Pixel-Level
  Anomaly Detection.}\\
  \textit{arXiv preprint arXiv:2407.06519}, 2024.
  \href{https://arxiv.org/abs/2407.06519}{\small[arXiv]}

\item \textbf{Hao Xu}, Juan Du\textsuperscript{\textdagger}, A.\ Wang, Y.C.\ Chen.\\
  \textbf{Ano-SuPs: Multi-size Anomaly Detection for Manufactured Products by
  Identifying Suspected Patches.}\\
  Under second revision at \textit{INFORMS Journal on Data Science}, 2023.
  \href{https://arxiv.org/abs/2309.11120}{\small[arXiv]}

\end{enumerate}

% ── SELECTED AWARDS ─────────────────────────────────────────
\section{Selected Awards}

\awardentry{Finalist, Best Paper Competition — INFORMS Conference on Quality, Statistics,
  and Reliability}{2025}

\awardentry{Outstanding Graduate of Chongqing City}{2020}

\awardentry{National College Students Summer Social Practice Special Action
  Bronze Award \textit{(Deputy Leader)}}{2018}

% ── (OPTIONAL SECTIONS — uncomment and fill in as needed) ───

% \section{Research \& Work Experience}
% \edentry{Research Assistant}{...}{...}{...}

% \section{Skills}
% \begin{itemize}
%   \item \textbf{Programming:} Python, MATLAB, R, \LaTeX
%   \item \textbf{Frameworks:} PyTorch, HuggingFace, Open3D
%   \item \textbf{Languages:} Chinese (native), English (fluent)
% \end{itemize}

% \section{Academic Service}
% \begin{itemize}
%   \item Reviewer, \textit{...}
% \end{itemize}

\end{document}
